Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-08-12 02_paper/02_study/01_eye tracking video questionnaire paper/paper_methods.Rmd
Update paper_methods.Rmd

A theory-based coding scheme was developed as an observation tool for classroom observation. The coding of the reactions was done in seven levels. Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping (cf. Kounin 2006; Gold & Holodynski 2015) by not interrupting the flow of instruction. Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response. A brief, timely, and purposeful rebuke of the disruptive student is considered by Kounin (2009, p. 99), among others, to be an important component of the strategy of presence and thus demonstrates good classroom management. If the teacher reacts non-verbally and at the same time with a longer verbal statement, code 4 was assigned, because the flow of the lesson was already noticeably delayed. There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned. If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized (cf. Gold & Holodynski, 2015). If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned. According to Gippert et al. (2019), there is a relational error in such cases, as the intensity of the student response should be relative to the disruptive behavior (p. 2).

@@

With the help of scripted behavioral instructions for students in the instructional unit, a high degree of standardization was achieved that is not present in the normal school setting. The lessons were recorded with several video cameras from different angles and an audio recorder. This means a big advantage compared to the subjective evaluation of observers in real time. In addition, video recordings can be viewed multiple times, by different people or from different perspectives. Thus, a high measurement accuracy (reliability) is given (cf. Mayring, P., Gläser-Zikuda, M., & Ziegelbauer, 2005). All measures taken contribute to increase the validity of the method. However, it cannot be answered whether the coding scheme is completely valid, because a validation with the help of another measuring instrument was not possible. Therefore, it could not be controlled whether the collected construct is related to other similar constructs.

@@

*Monitoring* includes proactive strategies such as omnipresence. This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them. The second strategy is overlapping. In this case, the teacher is able to control several teaching processes at the same time. Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions (cf. ibid.; [@kounin2006techniken, p. 89ff).

By *managing momentum* (structuring), Gold and Holodynski (2015) understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p. 101ff]. They also include the group focus specifically identified by Kounin [@kounin2006techniken, p. 117ff], i.e. mobilizing the whole class and demanding accountability [@gold2015development, p. 231].

@@

Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management (SJT, [@gold2015development]) in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management. The completion of the entire survey took 15 min on average.

>>>>

A theory-based coding scheme was developed as an observation tool for classroom observation. The coding of the reactions was done in seven levels. Based on the literature on effective approaches to classroom disruptions, nonverbal response was given Code 1 as the best variant because it best accommodates the classroom management strategies of presence and overlapping [cf. @kounin2006techniken; @gold2015development] by not interrupting the flow of instruction. Code 2 or Code 3 was assigned for a brief verbal expression with or without a preceding nonverbal response. A brief, timely, and purposeful rebuke of the disruptive student is considered by Kounin (2009, p. 99), among others, to be an important component of the strategy of presence and thus demonstrates good classroom management. If the teacher reacts non-verbally and at the same time with a longer verbal statement, code 4 was assigned, because the flow of the lesson was already noticeably delayed. There were two possibilities, if there was no reaction: If the teacher deliberately ignored the disruption, code 5 was assigned. If the teacher did not notice the disruption, code 6 was assigned, because then no effective monitoring was realized [cf. @gold2015development].If the reaction to the disruption was dysfunctional, i.e., if the teacher shows an inappropriate reaction, such as explaining the class rules for a very long time in the case of an insignificant disruption, code 7 was assigned. According to Gippert et al. (2019), there is a relational error in such cases, as the intensity of the student response should be relative to the disruptive behavior (p. 2).

@@

With the help of scripted behavioral instructions for students in the instructional unit, a high degree of standardization was achieved that is not present in the normal school setting. The lessons were recorded with several video cameras from different angles and an audio recorder. This means a big advantage compared to the subjective evaluation of observers in real time. In addition, video recordings can be viewed multiple times, by different people or from different perspectives. Thus, a high measurement accuracy (reliability) is given [cf.@mayring2005auswertung]. All measures taken contribute to increase the validity of the method. However, it cannot be answered whether the coding scheme is completely valid, because a validation with the help of another measuring instrument was not possible. Therefore, it could not be controlled whether the collected construct is related to other similar constructs.

@@

*Monitoring* includes proactive strategies such as omnipresence. This means, the teacher is always informed about the students' behavior, regulates it and reports it back to them. The second strategy is overlapping. In this case, the teacher is able to control several teaching processes at the same time. Monitoring means also reactive strategies of supervision, which also includes the effective handling of classroom disruptions [cf. ibid.; @kounin2006techniken, p. 89ff].

By *managing momentum* (structuring), @gold2015development understand the skillful control of teaching processes so that they can run smoothly and without delays, taking into account the students' level of understanding and attention [@kounin2006techniken, p. 101ff]. They also include the group focus specifically identified by Kounin [@kounin2006techniken, p. 117ff], i.e. mobilizing the whole class and demanding accountability [@gold2015development, p. 231].

@@

Finally, the subjects answered a Situational Judgement Test of Strategic Knowledge of Classroom Management [SJT, @gold2015development] in the form of a questionnaire. Here they had to assess teaching scenarios and evaluate their behavior in response to them. The SJT was used to assess strategic knowledge about classroom management. The completion of the entire survey took 15 min on average.
